\begin{rubric}{Employment History}
\entry*[06/24 -- Present]
	\textbf{AOCS \& GNC Specialist} (Subsystem Leader), D-Orbit s.p.a., Como, Italy

    D-Orbit provides space logistics and satellite transportation solutions. As AOCS Subsystem Leader for the ION Satellite Carrier programme:
    \begin{itemize}
        \item Led development of AOCS software: attitude and orbit GNC algorithms and FDIR logic (sensor/actuator fault detection, isolation, and autonomous recovery), compliant with ECSS and Savoir guidelines; maintained the MATLAB/Simulink model-based design environment with code generation for FSW delivery.
        \item Executed the full V\&V pyramid: MIL, SIL, PIL, and HIL campaigns.
        \item Contributed to the ION-mk3 next-generation satellite: requirements flowdown, subsystem budgets, and system-level analyses.
        \item Supported ground-segment operations for LEO missions: telemetry monitoring, anomaly investigation, and mission analysis.
    \end{itemize}
%
\entry*[02/20 -- 06/24]
	\textbf{Co-Founder and CTO}, ANT-X s.r.l., Milan, Italy

    ANT-X is a PoliMi spin-off producing educational UAV platforms and research infrastructure for universities and laboratories worldwide. As CTO, I held full technical ownership across a team of 6:
    \begin{itemize}
        \item Designed and sized multirotor platforms from scratch (COTS components, custom frames) based on Pixhawk/PX4 architecture; customized the PX4 firmware to enable seamless deployment of MATLAB/Simulink code-generated GNC logic, allowing researchers to design, test, and fly control algorithms without writing C++.
        \item Integrated multi-environment localisation: outdoor GPS and indoor motion-capture and stereo-vision with an onboard companion computer for high-level autonomy.
        \item Delivered dozens of platforms annually to university research labs across Europe and the USA.
    \end{itemize}
%
\entry*[02/20 -- 10/20]
	\textbf{Post-Doctoral Researcher}, Department of Aerospace Science and Technologies, Politecnico di Milano, Italy. \textit{(Concurrent with ANT-X until full-time transition in 10/20.)}

    Research topics: Multirotor GNC, attitude and position control, model identification, parameter estimation, attitude and position estimation (EKF, complementary filter).
%
\entry*[03/19 -- 07/19]
	\textbf{Visiting Researcher}, LAAS - CNRS Toulouse, France.
 
   Research topics: Control allocation of fully-actuated and over-actuated multirotors.
%
\entry*[2018 -- 2019]
	\textbf{Teaching Assistant}, Department of Aerospace Science and Technologies, Politecnico di Milano, Italy.
 
   Assisted the lectures of the course "Estimation in Aerospace" for the M.Sc. tracks in Aeronautics and Space Engineering.
%
\entry*[01/16 -- 11/16]
	\textbf{Research Assistant}, Department of Aerospace Science and Technologies, Politecnico di Milano, Italy.

    Supported the drone laboratory after M.Sc. graduation; contributed to research activities that led to the first conference publication and the Ph.D. application.
%
\end{rubric}
